---
title: "index_construction"
author: "Zhuoran"
date: "31/12/2021"
output: html_document
---


#libraries
```{r}
library(foreign)
library(dplyr)
library(lubridate)
library(gbm)
library(pdp)
library(doParallel)
library(foreach)
library(ggplot2)
library(caret)
library(iml)
```



#global
#construct rppi, reference period is year 2004 Q1
#full period
```{r}
load("./full_period_index_lad_quarterly.RData")
#alt
#I could use Accumulated local effect rather than pdp, because it is faster and unbiased.
alt = Predictor$new(gbm_full, data = model) # this dataset need to use "model" in line 55, chunk 4.
alt_quarter = FeatureEffect$new(alt, feature = "quarter_num", grid.size = 100) # the `grid.size` is quite important, because it controls the outputs. I have 68 quarters in the data, then I have to change the grid.size to 68 (change it more to 100 for making sure, I can get 68 quarters), default is 20.
temp = data.frame(alt_quarter$results)
mlf_index_alt = data.frame(quarter = 1:68, index = 0)
mlf_index_alt$index = exp(temp$.value)/exp(temp$.value[1])*100
#save index
write.csv(mlf_index_alt, "./data/mlf_index_alt_quarterly.csv")
```



#rolling windows
```{r}
#load data
load("./rolling_window_index_lad_quarterly.RData")

model_train_hedonic = read.csv("./data/raw_data_2004_2020_RPPI_hedonic_train.csv")[-1]

model_train_hedonic$LA_DESC = as.factor(model_train_hedonic$LA_DESC)
model_train_hedonic$PROP_CLA = as.factor(model_train_hedonic$PROP_CLA)
model_train_hedonic$submarket = as.factor(model_train_hedonic$submarket)
model_train_hedonic$logprice = log(model_train_hedonic$SALE1)

model = data.frame(logprice = model_train_hedonic$logprice,
                   quarter_num = model_train_hedonic$quarter_num, 
                   LAND_ARE = model_train_hedonic$LAND_ARE, 
                   AREA_HSE = model_train_hedonic$AREA_HSE, 
                   age = model_train_hedonic$age, 
                   BEDS = model_train_hedonic$BEDS,
                   BATHS = model_train_hedonic$BATHS, 
                   DINING = model_train_hedonic$DINING, 
                   KITCHEN = model_train_hedonic$KITCHEN, 
                   FAMILY = model_train_hedonic$FAMILY, 
                   STUDY = model_train_hedonic$STUDY, 
                   GAMES = model_train_hedonic$GAMES, 
                   LOUNGE = model_train_hedonic$LOUNGE, 
                   MEALS = model_train_hedonic$MEALS, 
                   carpark = model_train_hedonic$carpark, 
                   LA_DESC = model_train_hedonic$LA_DESC, 
                   PROP_CLA = model_train_hedonic$PROP_CLA, 
                   centlong = model_train_hedonic$centlong, 
                   centlat = model_train_hedonic$centlat, 
                   TENCRT = model_train_hedonic$TENCRT,
                   d_pool = model_train_hedonic$d_pool, 
                   d_brick = model_train_hedonic$d_brick, 
                   d_tile = model_train_hedonic$d_tile)

#prepare windows for rolling process
for (i in 1:61) {
  temp_train = model[which(model$quarter_num <= (7+i) & model$quarter_num >= i),]
  
  assign(paste0("train_window_", i), temp_train)
}


#alt
#I could use Accumulated local effect rather than pdp, because it is faster and unbiased.
for (i in 1:61){
  temp_gbm = get(paste0("gbm_rolling_window_", i))
  temp_model = get(paste0("train_window_",i))
  alt = Predictor$new(temp_gbm, data = temp_model) # this dataset need to use "model" in line 55, chunk 4.
  alt_quarter = FeatureEffect$new(alt, feature = "quarter_num", grid.size = 20) # the `grid.size` is quite important, because it controls the outputs. I have 68 quarters in the data, then I have to change the grid.size to 68 (change it more to 100 for making sure, I can get 68 quarters), default is 20.
  temp = data.frame(alt_quarter$results)
  temp_mlr_index_alt = data.frame(quarter = i:(i+7), index = 0)
  temp_mlr_index_alt$index = exp(temp$.value)/exp(temp$.value[1])*100
  
  assign(paste0("mlr_index_alt_window_",i), temp_mlr_index_alt)
}


mlr_index_alt = data.frame(quarter = 1:68, index = 0)
mlr_index_alt$index[1:8] = mlr_index_alt_window_1$index
#chain the index
for (i in 2:61) {
  temp_mlr_index_alt = get(paste0("mlr_index_alt_window_",i))
  temp = temp_mlr_index_alt$index[8]/temp_mlr_index_alt$index[7]
  mlr_index_alt$index[i+7] = mlr_index_alt$index[i+6]*temp
}
#save index
write.csv(mlr_index_alt, "./data/mlr_index_alt_quarterly.csv")
```



#hedonic impute (cross section)
```{r}
#load data
load("./cross_section_window_index_lad_quarterly.RData")

model_train_hedonic = read.csv("./data/raw_data_2004_2020_RPPI_hedonic_train.csv")[-1]

model_train_hedonic$LA_DESC = as.factor(model_train_hedonic$LA_DESC)
model_train_hedonic$PROP_CLA = as.factor(model_train_hedonic$PROP_CLA)
model_train_hedonic$submarket = as.factor(model_train_hedonic$submarket)
model_train_hedonic$logprice = log(model_train_hedonic$SALE1)

model = data.frame(logprice = model_train_hedonic$logprice,
                   quarter_num = model_train_hedonic$quarter_num, 
                   LAND_ARE = model_train_hedonic$LAND_ARE, 
                   AREA_HSE = model_train_hedonic$AREA_HSE, 
                   age = model_train_hedonic$age, 
                   BEDS = model_train_hedonic$BEDS,
                   BATHS = model_train_hedonic$BATHS, 
                   DINING = model_train_hedonic$DINING, 
                   KITCHEN = model_train_hedonic$KITCHEN, 
                   FAMILY = model_train_hedonic$FAMILY, 
                   STUDY = model_train_hedonic$STUDY, 
                   GAMES = model_train_hedonic$GAMES, 
                   LOUNGE = model_train_hedonic$LOUNGE, 
                   MEALS = model_train_hedonic$MEALS, 
                   carpark = model_train_hedonic$carpark, 
                   LA_DESC = model_train_hedonic$LA_DESC, 
                   PROP_CLA = model_train_hedonic$PROP_CLA, 
                   centlong = model_train_hedonic$centlong, 
                   centlat = model_train_hedonic$centlat, 
                   TENCRT = model_train_hedonic$TENCRT,
                   d_pool = model_train_hedonic$d_pool, 
                   d_brick = model_train_hedonic$d_brick, 
                   d_tile = model_train_hedonic$d_tile)

#prepare windows for rolling process
for (i in 1:68) {
  temp_train = model[which(model$quarter_num == i),]
  
  assign(paste0("train_window_", i), temp_train)
}


#1t
dit_index_impute = data.frame(quarter = 1:68, rate = 1, index = 100)
#traditional method
for (i in 2:68){
  temp_pi = get(paste0("train_window_", i))
  temp_gbm = get(paste0("gbm_cross_section_window_", i))
  prediction_pi_t = predict(temp_gbm, temp_pi, n.trees = 2000)
  temp_pi$quarter_num = 1
  temp_gbm = get(paste0("gbm_cross_section_window_", 1))
  prediction_pi = predict(temp_gbm, temp_pi, n.trees = 2000)
  pi = exp(mean(prediction_pi_t - prediction_pi))
  #print(pi)
  
  temp_li = get(paste0("train_window_", 1))
  temp_gbm = get(paste0("gbm_cross_section_window_", 1))
  prediction_li = predict(temp_gbm, temp_li, n.trees = 2000)
  temp_li$quarter_num = i
  temp_gbm = get(paste0("gbm_cross_section_window_", i))
  prediction_li_t = predict(temp_gbm, temp_li, n.trees = 2000)
  li = exp(mean(prediction_li_t - prediction_li))
  #print(li)
  
  dit_index_impute$rate[i] = sqrt(pi*li)
  dit_index_impute$index[i] = dit_index_impute$rate[i]*100#prod(gbm_hedonic_index_impute$rate[1:(i+1)])*100
  print(i)
}
#save index
write.csv(dit_index_impute, "./data/dit_index_impute_1t_quarterly.csv")


#chained
dit_index_impute_chained = data.frame(quarter = 1:68, rate = 1, index = 100)
#traditional method
for (i in 2:68){
  temp_pi = get(paste0("train_window_", i))
  temp_gbm = get(paste0("gbm_cross_section_window_", i))
  prediction_pi_t = predict(temp_gbm, temp_pi, n.trees = 2000)
  temp_pi$quarter_num = i-1
  temp_gbm = get(paste0("gbm_cross_section_window_", i-1))
  prediction_pi = predict(temp_gbm, temp_pi, n.trees = 2000)
  pi = exp(mean(prediction_pi_t - prediction_pi))
  #print(pi)
  
  temp_li = get(paste0("train_window_", i-1))
  temp_gbm = get(paste0("gbm_cross_section_window_", i-1))
  prediction_li = predict(temp_gbm, temp_li, n.trees = 2000)
  temp_li$quarter_num = i
  temp_gbm = get(paste0("gbm_cross_section_window_", i))
  prediction_li_t = predict(temp_gbm, temp_li, n.trees = 2000)
  li = exp(mean(prediction_li_t - prediction_li))
  #print(li)
  
  dit_index_impute_chained$rate[i] = sqrt(pi*li)
  dit_index_impute_chained$index[i] = prod(dit_index_impute_chained$rate[1:(i)])*100
  print(i)
}
write.csv(dit_index_impute_chained, "./data/dit_index_impute_chained_quarterly.csv")
```






#local
#construct local rppis for each LGA, reference period is year 2004 Q1
#full period
```{r}
load("./full_period_index_lad_quarterly.RData")

lga = data.frame(table(model$LA_DESC))
mlf_index_alt = data.frame(quarter = rep(1:68,30), index = 0, lga = "")
n=0

for (i in lga$Var1) {
  #alt
  #I could use Accumulated local effect rather than pdp, because it is faster and unbiased.
  alt = Predictor$new(gbm_full, data = model[which(model$LA_DESC == i),]) # this dataset need to use "model" in line 55, chunk 4.
  alt_quarter = FeatureEffect$new(alt, feature = "quarter_num", grid.size = 1000) # the `grid.size` is quite important, because it controls the outputs. I have 68 quarters in the data, then I have to change the grid.size to 68 (change it more to 100 for making sure, I can get 68 quarters), default is 20.
  temp = data.frame(alt_quarter$results)
  
  
  mlf_index_alt$index[(n*68+1):(n*68+nrow(temp))] = exp(temp$.value)/exp(temp$.value[1])*100
  mlf_index_alt$lga[(n*68+1):(n*68+68)] = i
  n=n+1
}

#save index
write.csv(mlf_index_alt, "./data/mlf_local_index_alt_quarterly.csv")
```



#rolling windows
```{r}
#load data
load("./rolling_window_index_lad_quarterly.RData")

model_train_hedonic = read.csv("./data/raw_data_2004_2020_RPPI_hedonic_train.csv")[-1]

model_train_hedonic$LA_DESC = as.factor(model_train_hedonic$LA_DESC)
model_train_hedonic$PROP_CLA = as.factor(model_train_hedonic$PROP_CLA)
model_train_hedonic$submarket = as.factor(model_train_hedonic$submarket)
model_train_hedonic$logprice = log(model_train_hedonic$SALE1)

model = data.frame(logprice = model_train_hedonic$logprice,
                   quarter_num = model_train_hedonic$quarter_num, 
                   LAND_ARE = model_train_hedonic$LAND_ARE, 
                   AREA_HSE = model_train_hedonic$AREA_HSE, 
                   age = model_train_hedonic$age, 
                   BEDS = model_train_hedonic$BEDS,
                   BATHS = model_train_hedonic$BATHS, 
                   DINING = model_train_hedonic$DINING, 
                   KITCHEN = model_train_hedonic$KITCHEN, 
                   FAMILY = model_train_hedonic$FAMILY, 
                   STUDY = model_train_hedonic$STUDY, 
                   GAMES = model_train_hedonic$GAMES, 
                   LOUNGE = model_train_hedonic$LOUNGE, 
                   MEALS = model_train_hedonic$MEALS, 
                   carpark = model_train_hedonic$carpark, 
                   LA_DESC = model_train_hedonic$LA_DESC, 
                   PROP_CLA = model_train_hedonic$PROP_CLA, 
                   centlong = model_train_hedonic$centlong, 
                   centlat = model_train_hedonic$centlat, 
                   TENCRT = model_train_hedonic$TENCRT,
                   d_pool = model_train_hedonic$d_pool, 
                   d_brick = model_train_hedonic$d_brick, 
                   d_tile = model_train_hedonic$d_tile)

#prepare windows for rolling process
for (i in 1:61) {
  temp_train = model[which(model$quarter_num <= (7+i) & model$quarter_num >= i),]
  
  assign(paste0("train_window_", i), temp_train)
}

lga = data.frame(table(model$LA_DESC))
mlr_index_alt = data.frame(quarter = rep(1:68,30), index = 0, lga = "")
n=0

#alt
#I could use Accumulated local effect rather than pdp, because it is faster and unbiased.
for (j in lga$Var1) {
  for (i in 1:61){
    temp_gbm = get(paste0("gbm_rolling_window_", i))
    temp_model = get(paste0("train_window_",i))
    if (j != "PERTH CITY COUNCIL       " | i < 23){
      alt = Predictor$new(temp_gbm, data = temp_model[which(temp_model$LA_DESC == j),]) # this dataset need to use "model" in line 55, chunk 4.
      alt_quarter = FeatureEffect$new(alt, feature = "quarter_num", grid.size = 1000) # the `grid.size` is quite important, because it controls the outputs. I have 68 quarters in the data, then I have to change the grid.size to 68 (change it more to 100 for making sure, I can get 68 quarters), default is 20.
      temp = data.frame(alt_quarter$results)
      temp_mlr_index_alt = data.frame(quarter = i:(i+7), index = 0)
      temp_mlr_index_alt$index[1:nrow(temp)] = exp(temp$.value)/exp(temp$.value[1])*100
  
      assign(paste0("mlr_index_alt_window_",i), temp_mlr_index_alt)
    }
  }
  

  mlr_index_alt$index[(n*68+1):(n*68+8)] = mlr_index_alt_window_1$index
  #chain the index
  for (i in 2:61) {
    temp_mlr_index_alt = get(paste0("mlr_index_alt_window_",i))
    temp = temp_mlr_index_alt$index[8]/temp_mlr_index_alt$index[7]
    mlr_index_alt$index[n*68+i+7] = mlr_index_alt$index[n*68+i+6]*temp
  }
  mlr_index_alt$lga[(n*68+1):(n*68+68)] = j
  n=n+1
  print(n)
}

#save index
write.csv(mlr_index_alt, "./data/mlr_local_index_alt_quarterly.csv")
```



#hedonic impute (cross section)
```{r}
#load data
load("./cross_section_window_index_lad_quarterly.RData")

model_train_hedonic = read.csv("./data/raw_data_2004_2020_RPPI_hedonic_train.csv")[-1]

model_train_hedonic$LA_DESC = as.factor(model_train_hedonic$LA_DESC)
model_train_hedonic$PROP_CLA = as.factor(model_train_hedonic$PROP_CLA)
model_train_hedonic$submarket = as.factor(model_train_hedonic$submarket)
model_train_hedonic$logprice = log(model_train_hedonic$SALE1)

model = data.frame(logprice = model_train_hedonic$logprice,
                   quarter_num = model_train_hedonic$quarter_num, 
                   LAND_ARE = model_train_hedonic$LAND_ARE, 
                   AREA_HSE = model_train_hedonic$AREA_HSE, 
                   age = model_train_hedonic$age, 
                   BEDS = model_train_hedonic$BEDS,
                   BATHS = model_train_hedonic$BATHS, 
                   DINING = model_train_hedonic$DINING, 
                   KITCHEN = model_train_hedonic$KITCHEN, 
                   FAMILY = model_train_hedonic$FAMILY, 
                   STUDY = model_train_hedonic$STUDY, 
                   GAMES = model_train_hedonic$GAMES, 
                   LOUNGE = model_train_hedonic$LOUNGE, 
                   MEALS = model_train_hedonic$MEALS, 
                   carpark = model_train_hedonic$carpark, 
                   LA_DESC = model_train_hedonic$LA_DESC, 
                   PROP_CLA = model_train_hedonic$PROP_CLA, 
                   centlong = model_train_hedonic$centlong, 
                   centlat = model_train_hedonic$centlat, 
                   TENCRT = model_train_hedonic$TENCRT,
                   d_pool = model_train_hedonic$d_pool, 
                   d_brick = model_train_hedonic$d_brick, 
                   d_tile = model_train_hedonic$d_tile)

#prepare windows for rolling process
for (i in 1:68) {
  temp_train = model[which(model$quarter_num == i),]
  
  assign(paste0("train_window_", i), temp_train)
}


#1t
dit_index_impute = data.frame(quarter = rep(1:68,30), rate = 1, index = 100, lga = "")
#traditional method
lga = data.frame(table(model$LA_DESC))
n=0

for (j in lga$Var1) {
  dit_index_impute_temp = data.frame(quarter = 1:68, rate = 1, index = 100)
  for (i in 2:68){
    if (j != "PERTH CITY COUNCIL       " | i < 24){
      temp_pi = get(paste0("train_window_", i))
      temp_pi = temp_pi[which(temp_pi$LA_DESC == j),]
      temp_gbm = get(paste0("gbm_cross_section_window_", i))
      prediction_pi_t = predict(temp_gbm, temp_pi, n.trees = 2000)
      temp_pi$quarter_num = 1
      temp_gbm = get(paste0("gbm_cross_section_window_", 1))
      prediction_pi = predict(temp_gbm, temp_pi, n.trees = 2000)
      pi = exp(mean(prediction_pi_t - prediction_pi))
      #print(pi)
  
      temp_li = get(paste0("train_window_", 1))
      temp_li = temp_li[which(temp_pi$LA_DESC == j),]
      temp_gbm = get(paste0("gbm_cross_section_window_", 1))
      prediction_li = predict(temp_gbm, temp_li, n.trees = 2000)
      temp_li$quarter_num = i
      temp_gbm = get(paste0("gbm_cross_section_window_", i))
      prediction_li_t = predict(temp_gbm, temp_li, n.trees = 2000)
      li = exp(mean(prediction_li_t - prediction_li))
      #print(li)
  
      dit_index_impute_temp$rate[i] = sqrt(pi*li)
      dit_index_impute_temp$index[i] = dit_index_impute_temp$rate[i]*100#prod(gbm_hedonic_index_impute$rate[1:(i+1)])*100
    }
    print(i)
  }
  dit_index_impute$index[(n*68+1):(n*68+68)] = dit_index_impute_temp$index
  dit_index_impute$lga[(n*68+1):(n*68+68)] = j
  n=n+1
}

#save index
write.csv(dit_index_impute, "./data/dit_local_index_impute_1t_quarterly.csv")


#chained
dit_index_impute_chained = data.frame(quarter = rep(1:68,30), rate = 1, index = 100)
n=0

for (j in lga$Var1) {
  dit_index_impute_chained_temp = data.frame(quarter = 1:68, rate = 1, index = 100)
#traditional method
  for (i in 2:68){
    if (j != "PERTH CITY COUNCIL       " | i < 24){
      temp_pi = get(paste0("train_window_", i))
      temp_pi = temp_pi[which(temp_pi$LA_DESC == j),]
      temp_gbm = get(paste0("gbm_cross_section_window_", i))
      prediction_pi_t = predict(temp_gbm, temp_pi, n.trees = 2000)
      temp_pi$quarter_num = i-1
      temp_gbm = get(paste0("gbm_cross_section_window_", i-1))
      prediction_pi = predict(temp_gbm, temp_pi, n.trees = 2000)
      pi = exp(mean(prediction_pi_t - prediction_pi))
      #print(pi)
  
      temp_li = get(paste0("train_window_", i-1))
      temp_li = temp_li[which(temp_pi$LA_DESC == j),]
      temp_gbm = get(paste0("gbm_cross_section_window_", i-1))
      prediction_li = predict(temp_gbm, temp_li, n.trees = 2000)
      temp_li$quarter_num = i
      temp_gbm = get(paste0("gbm_cross_section_window_", i))
      prediction_li_t = predict(temp_gbm, temp_li, n.trees = 2000)
      li = exp(mean(prediction_li_t - prediction_li))
      #print(li)
  
      dit_index_impute_chained_temp$rate[i] = sqrt(pi*li)
      dit_index_impute_chained_temp$index[i] = prod(dit_index_impute_chained_temp$rate[1:(i)])*100
    }
    print(i)
  }
  dit_index_impute_chained$index[(n*68+1):(n*68+68)] = dit_index_impute_chained_temp$index
  dit_index_impute_chained$lga[(n*68+1):(n*68+68)] = j
  n=n+1
}

#save index
write.csv(dit_index_impute_chained, "./data/dit_index_local_impute_chained_quarterly.csv")
```
#step five: make 'load index' part seperately for global and local rppis, two chunks.
#test part in one chunk from the line 'model_resale = bulabula"





